---
title: "ADM"
author: "Błażej Orzechowski"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
---

## Libraries

```{r setup, echo=TRUE, message=FALSE, warning=FALSE, cache=T}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(ggplot2)
library(tidyr)
library(dplyr)
library(tibble)
library(plotly)
library(ggcorrplot)

set.seed(1)
```

## Import data

```{r}
data <- read.csv("data/mp_batteries.csv", sep=",", header=TRUE) %>%
  drop_na()

knitr::kable(head(data, 10))
```

-   **Battery.ID**: `character` - Unique battery identifier\
-   **Battery.Formula**: `character` - Chemical formula of battery\
-   **Working.Ion**: `character` - Primary working ion\
-   **Formula.Charge**: `character` - Formula in charged state\
-   **Formula.Discharge**: `character` - Formula in discharged state\
-   **Max.Delta.Volume**: `numeric` - Max volume change (%)\
-   **Average.Voltage**: `numeric` - Average operating voltage\
-   **Gravimetric.Capacity**: `numeric` - Capacity per unit mass\
-   **Volumetric.Capacity**: `numeric` - Capacity per unit volume\
-   **Gravimetric.Energy**: `numeric` - Energy per unit mass\
-   **Volumetric.Energy**: `numeric` - Energy per unit volume\
-   **Atomic.Fraction.Charge**: `numeric` - Atomic fraction (charged)\
-   **Atomic.Fraction.Discharge**: `numeric` - Atomic fraction (discharged)\
-   **Stability.Charge**: `numeric` - Stability in charged state\
-   **Stability.Discharge**: `numeric` - Stability in discharged state\
-   **Steps**: `integer` - Number of transition steps\
-   **Max.Voltage.Step**: `numeric` - Largest voltage difference

## Basic statistics

```{r}
data %>% summarise(n())

data %>%
  summarise(across(where(is.numeric),
                   list(mean = ~mean(.),
                        median = ~median(.),
                        min = ~min(.),
                        max = ~max(.),
                        sd = ~sd(.),
                        n_unique = ~n_distinct(.)),
                   .names = "{col}_{fn}")) %>%
  pivot_longer(everything(), 
               names_to = c("statistic", "column"),
               names_sep = "_",
               values_to = "value") %>%
  pivot_wider(names_from = column, values_from = value) %>%
  knitr::kable()
```

## Data distributions

```{r}
data %>% 
  select(where(is.numeric)) %>%
  gather(key = "attribute", value = "value") %>%
  ggplot(aes(x = value)) +
  geom_histogram(bins = 30, fill = "lightblue", color = "black") +
  facet_wrap(~attribute, scales = "free") +
  theme_minimal() +
  labs(title = "Distribution of values", x = "Value", y = "Frequency")

```

## Correlations analysis

```{r}
numeric_columns <- data %>% select(where(is.numeric))
cor_matrix <- cor(numeric_columns, use = "complete.obs")

cor_data <- as.data.frame(as.table(cor_matrix))

# Interaktywny wykres
plot_ly(
  data = cor_data,
  x = ~Var1,
  y = ~Var2,
  z = ~Freq,
  zmin = -1,
  zmax = 1,
  type = "heatmap",
  colors = c("blue", "white", "red")
) %>%
  layout(
    title = "Correlation matrix",
    xaxis = list(title = ""),
    yaxis = list(title = "")
  )
```

## Trends

```{r}
ggplot(data, aes(x = Gravimetric.Capacity, y = Atomic.Fraction.Discharge)) +
  geom_point(alpha = 0.6, color = "blue") +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  facet_wrap(~ Working.Ion, scales = "free") +
  scale_y_continuous(limits = c(0, 1)) +
  scale_x_continuous(limits = c(0, 3000)) +
  labs(
    title = "Relationship between Gravimetric Capacity and Atomic Fraction Discharge",
    x = "Gravimetric Capacity",
    y = "Atomic Fraction Discharge"
  ) +
  theme_minimal()

```
